Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex
byword sheet

%Discuss the coefficients in the regression table
Call:
lm(formula = f ~ classifier + collocation + cooccurrence + base_word +     dependency_parsing + classifier:collocation + classifier:cooccurrence +     collocation:cooccurrence + collocation:dependency_parsing +     cooccurrence:dependency_parsing + collocation:cooccurrence:dependency_parsing,     data = plot.step.import())

Coefficients:
\begin{tabular}{l r}
                                (Intercept) & 0.5557355 \\
                                classifiert & 0.0444331  \\
                                 collocation & 0.0030636  \\
                              cooccurrence1 & 0.0276413 \\
                                 base_word1 & 0.0124008  \\
                         dependency_parsing & -0.0019423 \\
                     classifiert:collocation & -0.0132109 \\
                  classifiert:cooccurrence1 & -0.0271825 \\
                   collocation:cooccurrence1 & -0.0007417 \\
              collocation:dependency_parsing & -0.0003464 \\
           cooccurrence1:dependency_parsing & -0.1611043 \\
collocation:cooccurrence1:dependency_parsing & 0.0147078  \\
\end{tabular}

>>>>

%Discuss the coefficients in the regression table
